%-------------------------
% Resume in Latex
% Author : Gennadii Chursov
% Based off of: https://github.com/sb2nov/resume and https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Large \scshape Luis Emilio Santos Burgoa Suchomlinow} \\ \vspace{1pt}
    \small \textit{MS in Computational Analysis \& Public Policy Candidate} \\
    +1 312 296 3054 $|$ \href{mailto:lsantosb@uchicago.edu} {{\underline{lsantosb@uchicago.edu}}} $|$ \href{https://suchomlinow.github.io/luis.santosburgoa/}{\underline{Technical Portfolio}} $|$
    Chicago, IL
     %\href{https://github.com/namesurname}{\underline{github.com/namesurname}}
\end{center}

%-----------SUMMARY-----------
%\section*{Summary}
%Results-oriented and data-driven Automation Quality Engineer with a strong background in Java programming and a passion for ensuring software reliability. Experienced in designing, implementing, and executing automated test scripts to verify the functionality and performance of software applications. Proven track record of collaborating with development teams to identify and resolve issues early in the development process. Adept at utilizing testing frameworks such as JUnit and incorporating continuous integration tools like Jenkins. Skilled in creating and maintaining automated test suites for web and mobile applications. Committed to delivering high-quality software by applying industry best practices in testing and automation. Seeking opportunities to contribute technical expertise and enhance software development processes as an Automation Quality Engineer.

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {University of Chicago}{Chicago, United States}
      {MS in Computational Analysis \& Public Policy}{2025 - To date}
        \vspace{1mm}
      %\resumeSubheading
      %{Massachusetts Institute of Technology}{Cambridge, United States}
      %{Data, Economics, and Design of Policy: Public Policy - MicroMasters}%{2024- 2025}
        %\vspace{1mm}
    \resumeSubheading
      {University of Chicago}{Chicago, United States}
      {Policy Analytics Credential Program}{2024}
        \vspace{1mm}
    \resumeSubheading
      {Instituto Tecnológico Autónomo de México (ITAM)}{Mexico City, Mexico}
      {Plain Language and Effective Communication Diploma}{2023}
        \vspace{1mm}
      \resumeSubheading
      {Tecnológico de Monterrey}{Monterrey, Mexico}
      {Data Science For Business Diploma}{2023}
        \vspace{1mm} 
    \resumeSubheading
      {Instituto Tecnológico Autónomo de México (ITAM)}{Mexico City, Mexico}
      {Bachelor Degree in Industrial Engineering, ABET}{2015 - 2020}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
  {University of Chicago -- Research Assistant to Prof. Erin Kelley}{Feb 2025 -- Present}
  {Labor Market and Entrepreneurship Study}{Chicago, IL}
  \resumeItemListStart
    \resumeItem{Built reproducible Python workflows to clean pilot survey data and generate descriptive tables, figures, and summary statistics.}
    \resumeItem{Analyzed labor market profiles, entrepreneurship experience, technical skills, gender differences, and income expectations.}
    \resumeItem{Drafted research results.}
  \resumeItemListEnd

\resumeSubheading
  {Bank of Mexico -- Specialty Leader}{May 2023 -- Aug. 2025}
  {Economic Information Systems Office}{Mexico City, Mexico}
  \resumeItemListStart
    \resumeItem{Coordinated the publication process for flagship economic reports, ensuring consistency across text, tables, figures, charts, and maps.}
    \resumeItem{Supervised analysts and interns across economic research, editorial review, and publication workflows.}
    \resumeItem{Served as the main liaison for legal, transparency, compliance, non-financial risk, and internal audit matters within the Directorate General of Economic Research.}
    \resumeItem{Designed editorial and consistency guidelines to standardize the Quarterly Inflation Report.}
  \resumeItemListEnd

\resumeSubheading
  {Bank of Mexico -- Information and Business Analyst}{Nov. 2019 -- May 2023}
  {Economic Information Systems Office}{Mexico City, Mexico}
  \resumeItemListStart
    \resumeItem{Automated editorial and data-review workflows for flagship economic reports, reducing processing time and manual review steps.}
    \resumeItem{Produced analytic inputs, visualizations, tables, and data outputs for researchers and senior-level briefs.}
    \resumeItem{Developed the non-financial risk matrix for the Directorate General of Economic Research.}
  \resumeItemListEnd

    \resumeSubheading
    {Bank of Mexico - Internship}{Feb. 2019 -- Aug. 2019}
    {Deputy Manager's Office for Compliance and Process Monitoring}{Mexico City, Mexico}
        \resumeItemListStart
        \resumeItem{Assisted in monitoring compliance records and control activities for critical processes across the Bank of Mexico.}
        \resumeItem{Reviewed and organized documentation to support internal control, process monitoring, and institutional compliance efforts.}
    \resumeItemListEnd

    \resumeSubheading
      {ACCT (NGO) - Program Coordinator}{Jan. 2017 - Dec. 18}
      {Acción Comunitaria por la Colonia Tizapán}{Mexico City, México}
        \resumeItemListStart
            \resumeItem{Designed and coordinated the study plan for a community education program preparing students for high school admissions exams.}
            \resumeItem{Recruited, selected, and coordinated instructors for weekly remedial and exam-preparation classes.}
            \resumeItem{Supported program operations by aligning class content, teaching materials, and learning goals across instructors.}
        \resumeItemListEnd

    \resumeSubheading
      {Junior Exam Officer}{Feb. 2013 - Aug. 2015}
      {Rye School of English}{León, México}
      \resumeItemListStart
        \resumeItem{Responsible for managing Cambridge University international certificates, logistics, and institutional relationships for the regional venues.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming:}{ Python, R, SQL, Java, MATLAB, VBA (Excel Macros)} \\
     \textbf{Data \& ML Tools:}{ Stata, E Views, Power BI, Azure, Pentaho, GitHub} \\
    \textbf{Workflow:}{ Latex, JIRA, MS Office Suite} \\
    \textbf{Languages:} Spanish (Native), English (Fluent)
    }}
 \end{itemize}




%-----------Academic experience-----------
 \section{Academic Experience}
    \resumeSubHeadingListStart
     \resumeProjectHeading
        {\textbf{Board Member, Mexican Students Association} $|$ \emph{University of Chicago}}{Oct. 2025 - To date}
    \resumeProjectHeading
        {\textbf{Machine Learning, Artificial Intelligence \& Big data: Expert Panel} $|$ \emph{Deutsche Bundesbank}}{Sept. 2024}
    \resumeProjectHeading
        {\textbf{Policy communications: innovations and good practices} $|$ \emph{Bank of England}}{Jan. 2023}
     \resumeProjectHeading
        {\textbf{Masterclass in Data Visualization – Virtual Training by Andy Kirk} $|$ \emph{Data Viz Training}}{June 2022}
    \resumeProjectHeading
        {\textbf{Seminar on Data Visualization} $|$ \emph{INEGI}}{2022}
     \resumeProjectHeading
        {\textbf{President, Foreign Student´s Association} $|$ \emph{ITAM}}{Jan. 2018 - Dec. 2018}
    \resumeProjectHeading
        {\textbf{Treasurer, Foreign Student´s Association} $|$ \emph{ITAM}}{Jan. 2017 - Dec. 2017}
    \resumeProjectHeading
        {\textbf{President, Economic and Social Council} $|$ \emph{ITAMMUN}}{Jan. 2017 - Aug. 2017}        
   \resumeSubHeadingListEnd

%-----------Awards-----------
 \section{Awards}
    \resumeSubHeadingListStart
     \resumeProjectHeading
        {\textbf{Becker Friedman Institute Summer Research Fellowship} $|$ \emph{University of Chicago}}{April 2026}
    \resumeProjectHeading
        {\textbf{Harris Merit Scholarship} $|$ \emph{University of Chicago}}{September 2025}
     \resumeProjectHeading
        {\textbf{Graduate Scholarships Program} $|$ \emph{Bank of Mexico}}{June 2025}     
   \resumeSubHeadingListEnd

%-----------Publications-----------
\section{Publications}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Martínez, J. \& Santos Burgoa, L. “Avances y retos en la estrategia de comunicación de Banco de México: un análisis de los informes trimestrales.” Working Paper, 2023.} \\
     \textit{2023} \\
    }}

        \small{\item{
     \textbf{Santos Burgoa, L. "Los canales de transmisión de la política monetaria: diseño de un manual editorial y de buenas prácticas para las publicaciones en la banca central en México", Thesis, ITAM} \\
     \textit{2023} \\
    }}

        \small{\item{
     \textbf{Santos Burgoa, L. "El progreso desde la ingeniería", HolaMundo, Engineering and Technology Journal, v13.0} \\
     \textit{2018} \\
    }}

 \end{itemize}


%-----------Other-----------
\section{Other}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Barista and coffee workshop: Mexican Coffee Association} \\
     \textit{2024} \\
    }}
 \end{itemize}
%-------------------------------------------
\end{document}
